Analysing the effect of land-use type on the proportion of scouts

### 2021-11-16 analysis/landuse_effect_prop_scouts.Rmd
started work on updating figure

urban_plotdata <- plotdata[, 1:2]
urban_plotdata$`Land-use` <- "Urban"

```

@@

agri.rural.pls <- ggplot(data = plotdata, aes(x = Comp_.1, y = p)) +
  geom_point() +
  geom_line(data = newdat, aes(x = Comp_.1, y = fit)) +
  xlab("PC 1") +
  xlim(min(-2.5), max(3.))
agri.rural.pls
agrirural_plotdata <- plotdata[, 1:2]
agrirural_plotdata$`Land-use` <- "Agri-rural"

```

@@

ggsave(
  plot = agri_rural_fit,
  filename = "results/figures/agrirural_fit.png",
  width = 183,
  height = 190,
  units = "mm",
  dpi = 300
)

```

>>>>

urban_plotdata <- plotdata[, 1:2]
urban_plotdata$`Land-use` <- "Urban"
```

@@

agri.rural.pls <- ggplot(data = plotdata, aes(x = Comp_.1, y = p)) +
  geom_point() +
  geom_line(data = newdat, aes(x = Comp_.1, y = fit)) +
  xlab("PC 1") +
  xlim(min(-2.5), max(3.))
agri.rural.pls
agrirural_plotdata <- plotdata[, 1:2]
agrirural_plotdata$`Land-use` <- "Agri-rural"
```

@@

ggsave(
  plot = agri_rural_fit,
  filename = "results/figures/agrirural_fit.png",
  width = 183,
  height = 190,
  units = "mm",
  dpi = 300
)
```

## Land-use maps

```{r, agrirural_landuse_maps, message = FALSE, warning = FALSE}
library(sf)
library(sp)
library(ggspatial)

# make fit map with agrirural landuses
agrirural_plotdata$site <- rural_lu$site
agrirural_plotdata$prop_scouts <- rural_lu$p
ar_sortedpropscouts <- arrange(agrirural_plotdata, prop_scouts)
ar_marked <- ar_sortedpropscouts[
  c(1, nrow(ar_sortedpropscouts) / 2, nrow(ar_sortedpropscouts)),
]

# make model fit graph of pc1 against prop scouts and mark the sites with the
# lowest, middle and highest proportion of scouts
ar_fit <- ggplot(
  data = ar_sortedpropscouts, aes(x = Comp_.1, y = prop_scouts)
) +
  geom_point() +
  geom_point(
    data = ar_marked, aes(x = Comp_.1, y = prop_scouts, colour = "red")
  ) +
  geom_text(
    data = ar_marked, aes(x = Comp_.1, y = prop_scouts, label = site),
    nudge_x = c(0, 0), nudge_y = c(-0.05, -0.05), size = 8
  ) +
  geom_line(data = rural_fitdata, aes(x = Comp_.1, y = fit)) +
  geom_ribbon(
    data = rural_fitdata,
    aes(x = Comp_.1, y = fit, ymin = lower, ymax = upper),
    alpha = 0.2,
    fill = "deepskyblue"
  ) +
  theme(legend.position = "none") +
  xlab("PC 1") +
  ylab("Estimated proportion of scouts")

# make the maps for each of the sites selected in the previous step
site_shape_data <- list()
for (i in seq_len(3)) {
  path <- paste0(
    "shapefiles/agri-rural/",
    ar_marked[i, "site"], "/", ar_marked[i, "site"],
    ".shp"
  )
  df <- st_read(path) %>%
    st_transform(
      CRS("+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0")
    )
  site_shape_data[[ar_marked[i, "site"]]] <- df
}

site_shape_data$STU$descriptio

ggplot() +
  geom_sf(
    data = site_shape_data$STU
  )
```
